\input{setup}
\begin{document}
	\maketitle
	
	\section*{SKILLS}
	\begin{minipage}{0.5\textwidth}
		\centering
		\begin{itemize}
			\setlength \itemsep{0.1em}
			\item Power Electronics
			\item High-Density PCB Layout
			\item Embedded Systems
			\item C++, C, and Python Programming
			\item Data Structures and Algorithms
		\end{itemize}
	\end{minipage}%
	\begin{minipage}{0.5\textwidth}
		\centering
		\begin{itemize}
			\setlength \itemsep{0.1em}
			\item SPICE Circuit Simulation
			\item PCB Fabrication and Assembly Processes
			\item Electronics Lab Equipment
			\item Hardware and Software Debugging
			\item Technical Documentation; LaTeX
		\end{itemize}
	\end{minipage}
	
	\section*{PROJECTS}
	\subsection{SinESC}
	Electronic motor speed controller (ESC) for drones. Supports sensorless field-oriented control for maximal power efficiency.
	\subsection{Universal Laser Driver}
	Low-power laser driver with ultra-wide input and output voltage range. Also built laser pointers of various wavelengths using the Universal Laser Driver.
	\subsection{Soldering Guide}
	Comprehensive guide for soldering through-hole components by hand.
	\subsection{RC Drones and Planes}
	Built and flew remote-controlled drones and planes – primarily first-person-view drones, glider-style airplanes, and nitromethane-powered airplanes. Set up autopilot systems and Iridium satellite communications channel for a solar-powered airplane intended to sustain flight for multiple days.
	\subsection{Solid-State Tesla Coil}
	Converts line voltage to several hundred kilovolts, generating foot-long electrical arcs. Used to demonstrate high voltage and electromagnetic induction.
	
	\section*{EDUCATION}
	UC Santa Barbara – B.S., Electrical Engineering (2022–2026)
	
	\section*{EXPERIENCE}
	Student Worker – Instructional Lab Group, UCSB Department of Physics (April 2023–present)
	\begin{itemize}
		\setlength \itemsep{0.1em}
		\item Set up labs for all undergraduate physics courses.
		\item Managed inventory; repaired broken equipment.
		\item Documented lab procedures.
		\item Designed electronics projects to be incorporated into lab curriculum.
	\end{itemize}
\end{document}
